\documentclass[../main.tex]{subfiles}
\begin{document}

\section{Tài liệu tham khảo}

Danh sách tài liệu tham khảo được trình bày theo định dạng IEEE.

\vspace{1cm}

\textbf{Các công trình chính liên quan đến đồ án:}

\begin{itemize}
    \item Latimer, C., et al. (2025). HINDSIGHT: Long-Term Memory for Conversational Agents. Đây là baseline chính cho đồ án.
    
    \item Wu, Y., et al. (2025). LongMemEval-S: Benchmark for Long-Term Memory in Conversational Agents.
    
    \item Maharana, A., et al. (2024). LoCoMo: Long-Context Memory Evaluation Benchmark.
    
\end{itemize}

\vspace{1cm}

\textbf{Các công trình về cơ sở khoa học nhận thức:}

\begin{itemize}
    \item Tulving, E. (1972). Episodic and Semantic Memory. Định nghĩa Semantic Memory.
    
    \item Tulving, E. (1983). Elements of Episodic Memory. Định nghĩa Episodic Memory.
    
    \item Squire, L. R., \& Zola-Morgan, S. (1991). The Medial Temporal Lobe Memory System. Phân loại các hệ con bộ nhớ.
    
    \item Dickinson, A., \& Balleine, B. (1994). Motivational Control of Goal-Directed Action. Devaluation test cho S-R vs A-O.
    
    \item Baddeley, A. D. (2000). The Episodic Buffer: A New Component of Working Memory? Giới thiệu Episodic Buffer.
    
    \item Brandimonte, M. A., et al. (1996). Prospective Memory. Lý thuyết về Prospective Memory.
    
    \item Hommel, B., et al. (2001). The Theory of Event Coding (TEC). Cơ sở cho Action-Effect Network.
    
    \item Brainerd, C. J., \& Reyna, V. F. (2004). Fuzzy Trace Theory. 2-layer representation (gist vs verbatim).
    
    \item Hodgkin, A. L., \& Huxley, A. F. (1952). A Quantitative Description of Membrane Current. Local refractoriness.
    
    \item Wilson, H. R., \& Cowan, J. D. (1972). Excitatory and Inhibitory Interactions in Localized Populations. Saturation threshold.
\end{itemize}

\vspace{1cm}

\textbf{Các công trình về memory systems và AI agents:}

\begin{itemize}
    \item Packer, C., et al. (2023). MemGPT: Towards LLMs as Operating Systems. Memory management paradigm.
    
    \item Rosch, E. (1978). Principles of Categorization. Basic Level Categorization.
    
    \item Bartlett, F. C. (1932). Remembering: A Study in Experimental and Social Psychology. Schema Theory.
\end{itemize}

\end{document}